%!TEX program = xelatex
\documentclass[10pt, a4paper]{article}

% Import my resume package
\usepackage{../../neatresume}

% Page layout
\usepackage{geometry}
\geometry{a4paper,margin=0.6in}
%\geometry{showframe} % For debugging

\usepackage{graphicx}
\usepackage{float}
\usepackage[hidelinks]{hyperref}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{array}
\usepackage{longtable}
\usepackage{enumitem}

% Link settings
\definecolor{MyLinkColor}{HTML}{2c82c9}
\hypersetup{
    colorlinks=false,
    citecolor=MyLinkColor,
    linkcolor=MyLinkColor,
    filecolor=MyLinkColor,
    urlcolor=MyLinkColor
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

% Disable page numbering
\pagenumbering{gobble}

\definecolor{MyDelimiterColor}{HTML}{cccccc}

\begin{document}
    
    % Title
    \mytitle{Your Name}
    
    % Meta info
    \setlength\tabcolsep{0pt}
    \begin{tabular}{lll}
        \email{success@company.com}\hspace*{1.8cm}
        &
        \phone{(+86) 189-6666-xxxx}\hspace*{1.8cm}
        &
        \github{https://github.com/neo-derek}{neo-derek}
    \end{tabular}
    \vspace*{8pt}
    
    % Education
    \mysection{Education}
    
    \mysubsection{Tongji University}
    
    MSc Software Engineering \hfill 20xx.9 --- 20xx.6
    
    \mydelimiter
    
    \mysubsection{Tongji University}
    
    BCs Software Engineering \hfill 20xx.9 --- 20xx.6
    
    \mydelimiter
    
    % Experience
    \mysection{Internship}
    
    \mysubsection{Google Shanghai}
    
    Software Development Intern \hfill 2018.6 --- 2018.12
    
    \begin{itemize}[leftmargin=*, topsep=0pt]
        \item Major work: participated in the development of some cloud service system, responsible for some functionality.
        \item Major achievements: used some technology to tackle some tricky problem under some scenario.
        \item Technologies: Apache RocketMQ, Hadoop, Spark, and PostgreSQL.
    \end{itemize}
    
    \mydelimiter
    
    \mysubsection{Microsoft Shanghai}
    
    Some Lab\hspace*{1em}Intern \hfill 2017.5 --- 2017.9
    
    \begin{itemize}[leftmargin=*, topsep=0pt]
        \item Major work: participated in the development of some cloud service system, responsible for some functionality.
        \item Major achievements: used some technology to tackle some tricky problem under some scenario.
        \item Technologies: Apache RocketMQ, Hadoop, Spark, and PostgreSQL.
    \end{itemize}
    
    \mydelimiter
    
    % Software projects
    \mysection{Software Projects}
    
    \mysubsection{Some APP}
    
    Android Development \hfill 2017.9 --- 2017.11
    
    \begin{itemize}[leftmargin=*, topsep=0pt]
        \item Introduction: some APP is a mobile application which enables users to 
        \item Major work: implemented the danmu functionality in the live video page; refined the user profile page; optimized the APP startup speed
        \item Technologies: Android, MVVM architecture
    \end{itemize}
    
    \mydelimiter
    
    \mysubsection{NeatResume}
    
    NeatResume is an elegant, neat and open-source resume template, using \LaTeX{} for typesetting.
    
    \begin{itemize}[leftmargin=*, topsep=0pt]
        \item GitHub address: \href{https://github.com/neo-derek/neat-resume}{\courierprime\fontsize{10}{12}\selectfont https://github.com/neo-derek/neat-resume}
    \end{itemize}
    
    \mydelimiter
    
    % IT Skills
    \mysection{IT Skills}
    
    \begin{itemize}[leftmargin=*, topsep=0pt]
        \item Programming languages: familiar with Java, Python; used Kotlin, JavaScript, C++, C, and Rust.
        \item Frameworks: familiar with Android, Spring Boot, MyBatis, MySQL, and Vue.js; used PostgreSQL, React, Redis, and RocketMQ.
    \end{itemize}
    
    % Honors and awards
    \mysection{Honors \& awards}
    
    \setlength\tabcolsep{0pt}
    \renewcommand{\arraystretch}{1.5}
    \begin{longtable}[l]{lll}
        2018 National Innovation and Entrepreneurship Contest & \hspace*{2em}\textbf{Gold Prize} & \hspace*{2em}National\\
        
        National Innovation and Entrepreneurship Training Program & \hspace*{2em}Graduation & \hspace*{2em}National\\
        
        2018 Mathematical Contest in Modeling (MCM) & \hspace*{2em}First Prize & \hspace*{2em}National\\
        
        2015 --- 2016 Tongji University Outstanding Undergraduate Student Scholarship & \hspace*{2em}First Prize & \hspace*{2em}University\\
    \end{longtable}
    
    % Personal summary
    \mysection{Personal Summary}
    
    The personal summary (or self-evaluation) part should be a comprehensive summary of yourself, aiming to let others know you better. In this section, emphasize the highlights you want to highlight, which are best related to your job seeking. This template only provides a format reference. The content and order inside need to be customized according to each person's personal situation and job-seeking wishes, so as to create a resume that really suits you. This r\'esum\'e template only ensures that your r\'esum\'e is up to the standard in terms of typesetting. Using this template only guarantees a lower limit of the r\'esum\'e; contents are more important than typesetting, and you need to be smart to present yourself based on your abilities and experience to improve the upper limit of your r\'esum\'e. Hope this template can help and enlight you. Please give it a star: \href{https://github.com/neo-derek/neat-resume}{\courierprime\fontsize{10}{12}\selectfont https://github.com/neo-derek/neat-resume}
    
    % Publications
    \mysection{Publications}
    
    \textbf{An Awesome Artificial Intelligence Framework}
    
    \textbf{Your. Name}, B. Bi, C. Cai, D. Du, E. Fu, in Proceedings of the 36th International Conference on Machine Learning (\textbf{ICML 2019}), CCF A class conference
    
    \mydelimiter
    
    \textbf{An Another Awesome Artificial Intelligence Framework}
    
    \textbf{Your. Name}, B. Bi, C. Cai, D. Du, E. Fu, in Proceedings of the 29th International Joint Conference on Artificial Intelligence (\textbf{IJCAI 2020}), CCF A class conference
    
    \mydelimiter
    
    % Miscellaneous
    \mysection{Miscellaneous}
    
    \begin{itemize}[leftmargin=*, topsep=0pt]
        \item English: proficient (TOEFL 120, CET--6 710)
        \item Personal website: \href{https://yourwebsite.com}{\courierprime\fontsize{10}{12}\selectfont https://yourwebsite.com}
    \end{itemize}
    
\end{document}
